One more attempt on ArXe

### 2016-01-27 exp_results.tex
add comments

\section{Experimental Results
\label{sec:exp_results}}
%
%
\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. 
Spectra of pure Ar and Xe clusters are included for reference. 
All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). 
Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. 
The average Xe content of the cluster ensemble, Xe$_{\rm cl}$, was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
Values for Ar 3p in the last row refer to the fine structure states.
\label{tab:valence} }
\begin{tabular}{ l c c c c c c c c}
%
\toprule
 \multicolumn{2}{r}{size} &  Xe$_{\rm in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
%
 \multicolumn{2}{r}{(label)}&  (\%) & Ar 3p & Ar 3p & Xe 5p$_{1/2}$ &  Xe 5p$_{3/2}$ & Xe 5p$_{3/2}$  &  (\%) \\
\midrule
% Ar, from Marko
 Ar & (1) &&  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar & (2) &&  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
 Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
%
\midrule
%
%  1004  886  (UHe, c.g. + roi values)
 ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
%
\midrule
% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Faﬂhauer <elke.fasshauer@uit.no>
 Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
%
 \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
%
\bottomrule
\end{tabular}
\end{table}

\subsection{Outer valence spectra}
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_oval_1.pdf}
 \caption{
Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
(a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). 
The two lower panels show spectra of the mixed species with different mean size. 
Sharp lines marked `m' result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower then the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
}
 \label{figure:oval1}
\end{figure}

@@

Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. 
Qualitatively similar spectra have been published without detailed discussion in Ref.\ \cite{lindblad}.
Differences are seen in particular for the Ar component. 
In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting. 
The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles,foerstel_arg1_2010} 
For larger clusters (e.g. $\langle N\rangle = 190$, black trace), the maximum at low binding energies becomes more pronounced, and is identified with emission from the cluster interior.\cite{hergenhahnprb,rolles}
At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV). 
For larger clusters (above $\langle N\rangle \approx 100$), it shows a dispersion characteristic for photoemission of crystalline bulk matter.\cite{foerstel_arg1_2010,foerstel_arg2_2011}

Ar 3p spectra of the mixed clusters show neither of these traits.
Rather, the Ar band is symmetric, less wide than in the pure clusters and at a higher binding energy. 
We characterize the spectral shape by giving a single value for the Ar 3p binding energy, and the FWHM of the feature.
Values for different expansion parameters, and for both Ar and Xe valence lines, are collected in Table\ \ref{tab:valence}.

@@

Emission from the Xe 5p state shows a much larger fine structure splitting, which dominates the spectrum even in clusters (where other broadening mechanisms are also present). 
For the mixed clusters, the Xe band broadens and shifts towards lower binding energy for larger size clusters. 
For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in Ref.\ \cite{lindblad}, Xe at $h\nu = 20$ eV in Ref.\ \cite{rolles}).
For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
At least for the 5p$_{1/2}$, this would be a seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.

@@

For the smallest clusters we have produced, a plausible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Fig.\ 7 in Ref.\ \cite{marques}).
We there see that for a Xe content of less than 60\,\%, core-shell systems are {\it not} formed, and although the Xe atoms tend to connect, the degree of Ar-Xe mixing is large.
While for low Xe content (approx. 10\,\%), some Ar atoms have only Ar nearest neighbours, for larger Xe content all Ar atoms seem to see both Ar and Xe nearest neighbours.
We believe this leads to the Ar 3p narrowing pointed out above.
Possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
If the scaling law size for a pure Ar expansion is taken as the lower limit for the cluster size, from the observed Xe content we arrive at clusters composed of a Xe core with four layers, covered by three layers of Ar (see Supporting Information).

Finally, comparing Figure \ref{figure:oval2} to \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur for changes in the expansion conditions than for changes of the gax mixture.
This finding is supported by the spectra shown in Ref.\ \cite{lindblad}.
%
%
\subsection{Inner valence spectra}
%
We now focus on the Ar inner valence (3s) vacancy states. 
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.8cm]{pics/figure_ival.pdf}
 \caption{
Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites'\protect\cite{hergenhahn2002}).
Colored symbols result from accumulating photoelectrons only from those events, which resulted in the subsequent emission of a second electron.
Solid lines represent various least-squares fits to the data, see text for details.
A photon energy of $h\nu = 32$ eV was used.
 \label{figure:ival}
 }
\end{figure}

@@

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_eff.pdf}
 \caption{
Efficiency of the decay of Ar 3s ionized states in ArXe clusters by emission of a secondary electron via ICD or ETMD. Values are arranged by Xe content of the initial gas mixture (`+' symbols: 1.2\,\%, asterisk: 3\,\%, triangle: 5\,\%). Symbol sizes indicate the photon energy (large symbols: 32 eV, small: 34 eV), and color indicates the cluster size (black symbols: S, red: M, blue: L). See text for details.
}
 \label{figure:eff}
\end{figure}
%
We now discuss which fraction of Ar 3s vacancy states relaxes via ICD or ETMD.
A method to derive this information has been established by some of us.\cite{foerstel_2013}
Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the 3s intensity in the undiscriminated spectrum.
The result gives the branching ratio of decay via ICD/ETMD vs. the sum of all channels, including those not involving electron emission.
To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with a very large widths.
The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the blue and red solid line in Figure \ref{figure:ival}.
Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events, corrected by the detection efficiency. 
This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}b. The corresponding figure for the ICD/ETMD efficiency is at one for \ref{figure:ival}a, and significantly smaller than one for \ref{figure:ival}b.
Figure \ref{figure:eff} shows the results of this analysis.
The error in the quantity shown is mainly determined by uncertainties in the peak/background separation.
(Our choice for the background shape is shown in Figure \ref{figure:ival}.)
For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different models.
Statistical errors are much smaller.

>>>>

\section{Experimental Results
\label{sec:exp_results}}
%
%
\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. 
Spectra of pure Ar and Xe clusters are included for reference. 
All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). 
Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. 
The average Xe content of the cluster ensemble, Xe$_{\rm cl}$, was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
Values for Ar 3p in the last row refer to the fine structure states.
\label{tab:valence} }
\begin{tabular}{ l c c c c c c c c}
%
\toprule
 \multicolumn{2}{r}{size} &  Xe$_{\rm in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
%
 \multicolumn{2}{r}{(label)}&  (\%) & Ar 3p & Ar 3p & Xe 5p$_{1/2}$ &  Xe 5p$_{3/2}$ & Xe 5p$_{3/2}$  &  (\%) \\
\midrule
% Ar, from Marko
 Ar & (1) &&  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar & (2) &&  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
 Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
%
\midrule
%
%  1004  886  (UHe, c.g. + roi values)
 ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
%
\midrule
% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Fa?hauer <elke.fasshauer@uit.no>
 Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
%
 \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
%
\bottomrule
\end{tabular}
\end{table}

\subsection{Outer valence spectra}
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_oval_1.pdf}
 \caption{
Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
(a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). 
The two lower panels show spectra of the mixed species with different mean size. 
Sharp lines marked `m' result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower then the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
 höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
 verschiedene CLustergrößen?}}
}
 \label{figure:oval1}
\end{figure}

@@

Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. 
Qualitatively similar spectra have been published without detailed discussion in Ref.\ \cite{lindblad}.
Differences are seen in particular for the Ar component. 
In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting. 
The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles,foerstel_arg1_2010} 
For larger clusters (e.g. $\langle N\rangle = 190$, black trace), the maximum at low binding energies becomes more pronounced, and is identified with emission from the cluster interior.\cite{hergenhahnprb,rolles}
At the particular photon energy selected here, atop of this band a sharp
feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of
about 1.8 eV). {\color{red}{Das Maximum ist bei etwa 1.8. Meinst du nicht oberhalb
von 1.8?}}
For larger clusters (above $\langle N\rangle \approx 100$),
it shows a dispersion {\color{red}{Was genau meinst du mit dispersion?}}
characteristic for photoemission of crystalline bulk matter.\cite{foerstel_arg1_2010,foerstel_arg2_2011}

Ar 3p spectra of the mixed clusters show neither of these traits.
Rather, the Ar band is symmetric,
less wide than in the pure clusters and at a higher binding energy.
{\color{red}{Wenn du dich auf panel b beziehst, dann kann das zwar sein, man sieht
es aber aus der Abbildung nicht. Kannst du das noch genauer belegen?}}
We characterize the spectral shape by giving a single value for the Ar 3p binding energy, and the FWHM of the feature.
Values for different expansion parameters, and for both Ar and Xe valence lines, are collected in Table\ \ref{tab:valence}.

@@

Emission from the Xe 5p state shows a much larger fine structure splitting, which dominates the spectrum even in clusters (where other broadening mechanisms are also present). 
For the mixed clusters, the Xe band broadens and shifts towards lower binding energy for larger size clusters. 
For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in Ref.\ \cite{lindblad}, Xe at $h\nu = 20$ eV in Ref.\ \cite{rolles}).
For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
At least for the 5p$_{1/2}$, this would be a seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
{\color{red}{Hier wäre es wichtig zu bemerken, dass es sich um die Bindungsenergie
 des Elektrons und nicht der Atome im Cluster handelt. Das hat mich an mehreren
 Stellen irritiert.}}

@@

For the smallest clusters we have produced, a plausible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Fig.\ 7 in Ref.\ \cite{marques}).
We there see that for a Xe content of less than 60\,\%, core-shell systems are {\it not} formed, and although the Xe atoms tend to connect, the degree of Ar-Xe mixing is large.
While for low Xe content (approx. 10\,\%), some Ar atoms have only Ar nearest neighbours, for larger Xe content all Ar atoms seem to see both Ar and Xe nearest neighbours.
We believe this leads to the Ar 3p narrowing pointed out above.
Possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
{\color{red}{Falsch. Für core-shell Strukturen müsste der Peak wieder breiter sein,
 da es dann wieder Argon Atome ohne Xenonnachbarn gibt (zumindest bei mehr als
 einer Argonschicht).}}
For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
If the scaling law size for a pure Ar expansion is taken as the lower limit for the cluster size, from the observed Xe content we arrive at clusters composed of a Xe core with four layers, covered by three layers of Ar (see Supporting Information).
{\color{red}{Dann sollten wir zumindest diesen Fall auch berechnen. Meinst du
$c=4$ oder 4 Schichten um ein Atom? -> Fehlt auch noch in supporting information}}

Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals
that much larger changes in the valence emission spectra occur for changes in
the expansion conditions than for changes of the gas mixture.
This finding is supported by the spectra shown in Ref.\ \cite{lindblad}.
%
%
\subsection{Inner valence spectra}
%
We now focus on the Ar inner valence (3s) vacancy states. 
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.8cm]{pics/figure_ival.pdf}
 \caption{
Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites'\protect\cite{hergenhahn2002}).
Colored symbols result from accumulating photoelectrons only from those events, which resulted in the subsequent emission of a second electron.
Solid lines represent various least-squares fits to the data, see text for details.
A photon energy of $h\nu = 32$ eV was used.
 \label{figure:ival}
 }
\end{figure}

@@

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_eff.pdf}
 \caption{
Efficiency of the decay of Ar 3s ionized states in ArXe clusters by emission of a secondary electron via ICD or ETMD. Values are arranged by Xe content of the initial gas mixture (`+' symbols: 1.2\,\%, asterisk: 3\,\%, triangle: 5\,\%). Symbol sizes indicate the photon energy (large symbols: 32 eV, small: 34 eV), and color indicates the cluster size (black symbols: S, red: M, blue: L). See text for details.
}
 \label{figure:eff}
\end{figure}
%
We now discuss which fraction of Ar 3s vacancy states relaxes via ICD or ETMD.
A method to derive this information has been established by some of us.\cite{foerstel_2013}
Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the 3s intensity in the undiscriminated spectrum.
The result gives the branching ratio of decay via ICD/ETMD vs. the sum of all channels, including those not involving electron emission.
To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with very large widths.
The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the blue and red solid line in Figure \ref{figure:ival}.
Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events, corrected by the detection efficiency. 
This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}b. The corresponding figure for the ICD/ETMD efficiency is at one for \ref{figure:ival}a, and significantly smaller than one for \ref{figure:ival}b.
Figure \ref{figure:eff} shows the results of this analysis.
The error in the quantity shown is mainly determined by uncertainties in the peak/background separation.
(Our choice for the background shape is shown in Figure \ref{figure:ival}.)
For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different models.
Statistical errors are much smaller.
